---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, eval = FALSE}
library(plasticair)
plastic_data <- load_data()
```

This function loads the merged plastic waste and air quality dataset from the package.

```{r, eval = FALSE}
cleaned <- clean_plastics(plastic_data)
```

This function removes Grand Total summary rows, standardizes country name casing, and aggregates to one row per country-year.

```{r, eval = FALSE}
summarize_country_pollution(plastic_data, country_name = "Philippines")
```

This function creates a table showing total plastic waste and average AQI for a selected country. Default is the Philippines.

```{r, eval = FALSE}
summarize_top_countries(plastic_data, n = 10)
```

This function returns a table of the top N countries ranked by total plastic waste.

```{r, eval = FALSE}
plot_air_vs_plastic(plastic_data)
```

This function creates a bubble plot comparing total plastic waste and average AQI across countries.

```{r, eval = FALSE}
animate_fertility_country(plastic_data)
```

This function creates an animated plot showing fertility rate over time for the Philippines.

```{r, eval = FALSE}
model <- run_plastic_aqi_lm(plastic_data)
```

This function fits a linear regression of average AQI on total plastic waste and prints a coefficient table.
